The K2 Halo Photometry Campaign

### 2019-04-05 paper/ms.tex
quality flags

In addition to these changes in objective function, we have also added a feature `\texttt{deathstar}' to deal with contamination. We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out. \textcolor{red}{More here from Tim.}

>>>>

In addition to these changes in objective function, we have also added a feature `\texttt{deathstar}' to deal with contamination. We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out. \textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion. We now iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
